Sample-Efficient Reinforcement Learning \\ with Implicitly Quantized Representations

### 2024-02-02 paper/main.tex
Code mentioned

% Arno recommends to have this here as a last thing (leaves a positive feeling)
A reference implementation of the methods and benchmarking setup will be made available on GitHub upon acceptance of the paper (see supplementary material for now).

>>>>

% Arno recommends to have this here as a last thing (leaves a positive feeling)
A reference implementation of the methods will be made available on GitHub upon acceptance of the paper (see supplementary material for now).
